### 2024-10-01 Manuscript/supplementaries.tex
Update supplementaries.tex

>>>>

\subsection{Glossary}

\begin{table}[ht]
\caption{Glossary and equivalence of terms used in this papers; adapted from \cite{guillerme2018disprity} and \cite{mammola2021concepts}.}
\centering
\begin{tabular}{p{2.5cm}p{4cm}p{5cm}p{5cm}}
Term in this paper & definition & in ecology & in macroevolution \\
\hline
Trait space & Matrix ($n \times d$) with a structural relation between rows and columns & Functional space, morphospace , etc. & Morphospace, traitspace, etc.  \\
\hline
Observations & Rows ($n$) & Taxa, field sites, environments, etc. & Taxa, specimen, populations, elements, OTUs etc. \\
\hline
Dimensions & Columns ($d$) & Traits, Ordination scores, distances, etc. & Traits, ordination scores, distances, etc. \\
\hline
Traits & Columns subset ($b \times n$; $b \leq d$) & uni/multidimensional trait; e.g. geographical location & uni/multidimensional trait; e.g. landmark coordinates \\
\hline
Group & Rows subset ($m \times d$; $m \leq n$) & Treatments, phylogenetic group (clade), etc. & Clades, geological stratum, etc. \\
\hline
Metric & Statistic (i.e. a measure) & Dissimilarity index or metric, hypervolume, functional diversity, etc. & Disparity metric or index \\
\hline
Stressors & An algorithm removing a proportion of the observations & Introduction of invasive species, change of landscape use, climate change, pollution, experimental design, etc. & Mass extinction, Tectonic change, climate change, etc. \\
\hline
Stressors' strength & The amount of observation removed (percentages) & Proportion of species affected, proportion of temperature change, etc. & Severity of mass extinction,  etc. \\
\end{tabular}
\end{table}
